Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-14 krs-survey.tex
Filled section on intrinsic motivation

\subsubsection{Intrinsic Motivation}

\cite{Oudeyer2007} -> page 2 gives a detailled account of psychological grounds.
Curiosity, Pro-active behaviour...

>>>>

\subsubsection{Intrinsic Motivation and Curiosity}

The reason for a robot to acquire knowledge are various, and usually external
to the robot itself. It is often driven by the needs of the tasks the robot has
to execute. In this case, motivations are managed by the execution controler
and are mostly unvisible to the knowledge representation system.

However, motivation can also be intrinsic, driven by the internal state of the
robot, without external pressure or reward. In this case, the

In the context of robotics, Oudeyer notes however that \emph{the information that is
compared \emph{[to compute a level of motivation]} has to be understood in an
information theoretic perspective, in which what is considered is the intrinsic
mathematical structure of the values of stimuli, independently of their
meaning.}~\cite{Oudeyer2007}.

Psychological grounds of motivation are summarized in~\cite{Oudeyer2007} while
the main approaches to computational motivation, divided into knowledge based
models, competence based models and morphological models, are surveyed
in~\cite{Oudeyer2008}.
